### 2014-11-13 abstract.tex
small edit

Declarative programming has been hailed as a promising approach to parallel
programming since it hides the implementation details of parallelism away from
the programmer. However, its advantage has also been its downfall as it leaves
the programmer with no straightforward way to optimize programs for performance.
In this paper, we introduce Coordinated Linear Meld, a concurrent
forward-chaining linear logic programming language, with a declarative way to
coordinate the execution of the program allowing the programmer to change
computation scheduling and data layout. Our approach allows the programmer to
write graph-based declarative programs and then optionally use coordination to fine
tune performance, while keeping the program fully declarative and easy to reason
about.

>>>>

Declarative programming has been hailed as a promising approach to
parallel programming since it hides the implementation details of
parallelism from the programmer. However, its advantage has also been
its downfall as it leaves the programmer with no straightforward way
to optimize programs for performance.  In this paper, we introduce
Coordinated Linear Meld, a concurrent forward-chaining linear logic
programming language, with a declarative way to coordinate the
execution of the program allowing the programmer to change computation
scheduling and data layout. Our approach allows the programmer to
write graph-based declarative programs and then optionally use
coordination to fine tune performance, while keeping the program fully
declarative and easy to reason about.
